### 2019-02-26 sections/intuition.tex
make it clearer what partial function means
by giving an example with bottom

Several observations can be made about tasks.
One of those is determining the value of a task $\Value(t)$. \fixme{Should we change the type of Value to Maybe v? Both johan and alejandro mention that it is not completely clear to them.}
Not all tasks have a value, for example the empty editor $\Enter \tau$, which makes $\Value$ a partial function.

>>>>

Several observations can be made about tasks.
One of those is determining the value of a task $\Value(t)$.
% \fixme{Should we change the type of Value to Maybe v? Both johan and alejandro mention that it is not completely clear to them.}
% I don't think that we should use Maybe. We should use the term partial function and bottom. -- mkl
Not all tasks have a value, for example the empty editor $\Enter \tau$, which makes $\Value$ a partial function.
For example, $\Value(\Edit 5) = 5$, $\Value(\Enter \Int) = \bot$.
